%------------------ Class ------------------%
\documentclass[a4paper,11pt]{article}

%------------------ Packages ------------------%
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

% Helvetica / sans look
\usepackage[scaled=0.92]{helvet}
\renewcommand{\familydefault}{\sfdefault}

\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage[a4paper,margin=1.7cm]{geometry}

%------------------ Formatting ------------------%
\setlength{\parskip}{2pt}
\setlength{\parindent}{0pt}
\renewcommand{\baselinestretch}{0.97}
\titleformat{\section}{\large\bfseries\color{blue}}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\normalsize\bfseries}{}{0em}{}[]
\setlist[itemize]{left=1.2em, itemsep=2pt, topsep=2pt}

% Section title spacing
\titlespacing*{\section}{0pt}{10pt plus 2pt minus 2pt}{8pt}
\titlespacing*{\subsection}{0pt}{8pt plus 1pt minus 1pt}{6pt}

%------------------ PDF Export Settings ------------------%
\usepackage{hyperref}
\hypersetup{
    pdfauthor={Luke Edgecombe},
    pdftitle={Luke Edgecombe - CV},
    pdfsubject={Curriculum Vitae - Robotics and Machine Learning Engineer},
    pdfkeywords={Robotics, Machine Learning, Control Systems, Heriot-Watt, Engineering, Python, ROS, MLP, IoT},
    pdfproducer={LaTeX with hyperref},
    pdfcreator={pdflatex},
    colorlinks=false,        % keep links hidden (already using hidelinks)
    pdfborder={0 0 0}
}

% Optimize PDF size and compression
\pdfcompresslevel=9
\pdfobjcompresslevel=3


%------------------ Header ------------------%
\begin{document}
\begin{center}
    {\LARGE \textbf{Luke Edgecombe}} \\[4pt]
    \href{mailto:luke.edgecomb2@gmail.com}{luke.edgecomb2@gmail.com} \,|\, +44 7465 433217 \,|\, Edinburgh, UK \\
    \href{https://linkedin.com/in/luke-edgecombe333}{linkedin.com/in/luke-edgecombe333} \,|\, 
    \href{https://github.com/Luk446}{github.com/Luk446}
\end{center}

\vspace{0.3cm}

%========================================================%
\section*{About Me}
Robotics and machine-learning engineer with a background in biomedical engineering. I am currently studying for an \textbf{MSc in Robotics with Industrial Application} at Heriot-Watt University (expected 2027), focusing on end-to-end IoT systems, ML theory, ROS programming, and robot kinematics. My undergraduate thesis explored automatic hyperparameter optimisation for an MLP regressor controlling a prototype soft medical robot. I am seeking a six-month industry placement to apply ML and control-systems expertise to real-world robotics challenges.

%========================================================%
\section*{Education}

\textbf{MSc Robotics with Industrial Application} \hfill \textbf{2025--2027 (expected)}\\
\textit{Heriot-Watt University, Edinburgh, UK}
\begin{itemize}
    \item \textbf{Current modules:} End-to-End IoT Systems, Machine-Learning Theory, ROS Programming, and Robot Kinematics.
    \item Developing applied skills in robotics software stacks and system integration.
\end{itemize}

\textbf{BEng Biomedical Engineering (First Class Honours)} \hfill \textbf{2021--2025}\\
\textit{University of Dundee, Dundee, UK}
\begin{itemize}
    \item \textbf{Key modules:} Software Applications for Biomedical Engineering, Medical Instrumentation, Electronics and Instrumentation, Biomechanics and Biomaterials.
    \item \textbf{Final-year thesis:} Automatic HPO for MLP Regressor in Soft Medical Robotics.
    \item \textbf{Award:} Open Prize for Biomedical Engineering (2022)
\end{itemize}

%========================================================%
\section*{Selected Projects}

\textbf{Automatic HPO for MLP Regressor in Soft Medical Robotics} \hfill \textit{Undergraduate Degree Thesis}
\begin{itemize}
    \item Implemented an MLP regressor mapping position inputs to actuation outputs for a soft-robotics prototype.
    \item Designed an automatic hyperparameter-optimisation pipeline improving model accuracy and training efficiency with limited data.
    \item Addressed real-world constraints including non-linear kinematics and small datasets.
\end{itemize}

\textbf{Medical Image Classification} \hfill \textit{Postgraduate Team Project}
\begin{itemize}
    \item Classifying MRI images for identifying brain pathology.
\end{itemize}

\textbf{A-Star Path Planning} \hfill \textit{Postgraduate Project}
\begin{itemize}
    \item Developed path planning systems for virtual robotic systems using the A-star algorithm.
\end{itemize}

\textbf{ESP32 Cloud IoT Platform}
\begin{itemize}
    \item Communicate with an MQTT broker to stream environmental data.
    \item Using node-red platform.
\end{itemize}

\textbf{Össur Upper-Limb Prosthesis (Industry-Linked)} \hfill \textit{Undergraduate Project}
\begin{itemize}
    \item Contributed to mechanical design and user-application development for an upper-limb prosthesis.
    \item Focused on improving mechatronic design workflow and end-user interaction.
\end{itemize}

\textbf{Automated Endo-Robotic Solution} \hfill \textit{Undergraduate Team Project}
\begin{itemize}
    \item Developed an automated robotic platform for minimally invasive tasks.
    \item Led mechanical design and integrated calibration and sensor feedback systems.
\end{itemize}

\textbf{3D-Printed EMG Prosthetic Hand} \hfill \textit{Undergraduate Team Project}
\begin{itemize}
    \item Designed and manufactured a low-cost prosthetic hand controlled using EMG signals.
    \item Applied biomedical-engineering and embedded-system principles in a practical build.
\end{itemize}

\textbf{Laparoscopic Training Tool} \hfill \textit{Undergraduate Team Project}
\begin{itemize}
    \item Created an interactive laparoscopic-surgery training system providing user feedback.
    \item Focused on interface design and mechanical responsiveness.
\end{itemize}


%========================================================%
\section*{Technical Skills}

\begin{tabular}{@{}ll}
\textbf{Programming:} & Python, C++, C\#, MATLAB \\
\textbf{ML / Data:} & PyTorch, scikit-learn, hyperparameter optimisation, data processing \\
\textbf{Robotics:} & ROS, kinematics, control systems (PID), IoT integration \\
\textbf{Design \& CAD:} & SolidWorks (CSWA), Autodesk Inventor, 3D printing \\
\textbf{Other Tools:} & Git, Linux, LaTeX, VS Code
\end{tabular}

%========================================================%
\section*{Experience}

\textbf{Class Representative – University of Dundee} \hfill 2023--2025
\begin{itemize}
    \item Liaised between students and faculty to improve delivery and organisation of engineering modules.
    \item Gathered and presented student feedback, helping resolve course-related issues.
\end{itemize}

\textbf{Hospitality \& Events – Edinburgh Fringe (Underbelly, Assembly) \& Restaurants} \hfill 2018--2025
\begin{itemize}
    \item Worked in box-office, FOH, kitchen, and bar roles in high-pressure, time-sensitive environments.
    \item Developed teamwork, communication, and reliability under peak demand.
\end{itemize}

%========================================================%
\section*{Volunteering \& Activities}

\textbf{Retail Volunteer – Oxfam Shop} \hfill 1 year (during school)
\begin{itemize}
    \item Assisted with stock management, customer service, and daily operations.
    \item Built teamwork and responsibility in a customer-facing environment.
\end{itemize}

\textbf{STEM Ambassador – University of Dundee Ingenious Project}
\begin{itemize}
    \item Produced outreach materials promoting engineering and STEM pathways to school pupils.
\end{itemize}

\textbf{Mountaineering \& Outdoor Clubs}
\begin{itemize}
    \item Active member of mountaineering and mountain-biking societies.
    \item Planned and led trips emphasising safety, risk assessment, and communication.
\end{itemize}

%========================================================%
\section*{Certificates \& Awards}
\begin{itemize}
    \item Open Prize for Biomedical Engineering, University of Dundee (2022)
    \item CSWA – Certified SolidWorks Associate (2023)
    \item First Aid at Work (Ofqual Level 3)
\end{itemize}

%========================================================%
\section*{Interests}
Mountain and road biking, electronics, bouldering, rope climbing, and winter mountaineering.

\end{document}
